---
title: "Expressing Uncertainty"
output: html_document
date: "2022-10-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Expressing Uncertainty (15 points)

Topics to Cover:

Incorporating Data Variability in Graphs
Make sure to include:

(4 points) An introductory statement with the goal of the section (in your own words) and a brief description of the data set and variables you will be using.

(11 points) R code chunks interspersed with some text descriptions about the code you have written and with text description about each topic. For this section, you should actually make a graph (and not simply find an example already online like we looked at for hurricane graphs).

-----------------------------

This covers how to visualize data with variability so as not to exclude variability from the visual. I will use the gun violence data set, which has mortality and ownership rates of guns by state and region in America. 

-------------------------------

This plot visualizes an average, excluding all variability from the visual:
```{r}
library(tidyverse)
guns <- read_csv("data/gun_violence_us.csv")
  
ggplot(data = guns, aes(x = region, y = mean(mortality_rate))) +
  geom_col()
```

This plot shows more relevant features about the underlying data -- seeing both the mean and the variability via a boxplot:
```{r}
ggplot(data = guns, aes(x = region, y = mortality_rate)) +
  geom_boxplot()
```